Applied Measure Theory for Probabilistic Modeling

### 2022-05-12 paper/paper.tex
edits

In \verb|MeasureTheory|, a kernel is represented as either a Julia function or a \verb|TransitionKernel| object. The latter pairs a measure constructor with a mapping into its parameter space, and makes the functional relationship between argument of $\kappa$ and the returned measure transparent.

@@

@@

The above \verb|Likelihood| type is specified using a kernel and observed data. Though it is not an \verb|AbstractMeasure|, we include a \verb|logdensity| method for computational convenience. The core of the implementation is then
\begin{verbatim}
    struct Likelihood{F,S,X}
        k::Kernel{F,S}
        x::X
    end

    function logdensity(ℓ::Likelihood, p) 
        return logdensity(ℓ.k(p), ℓ.x)
    end
\end{verbatim}

>>>>

In \verb|MeasureTheory|, a kernel is represented as either a Julia function or an \verb|AbstractTransitionKernel| object. 
As a common special case, a \verb|ParameterizedTransitionKernel| pairs a measure constructor with a mapping into its parameter space, and makes the functional relationship between argument of $\kappa$ and the returned measure transparent.

@@

\chad{I think our adoption of DensityInterface complicates this section - needs some review}

@@

The above \verb|Likelihood| type is specified using a kernel and observed data. Though it is not an \verb|AbstractMeasure|, we include a \verb|logdensity| method for computational convenience. The core of the implementation is then
\begin{verbatim}
    struct Likelihood{F,S,X}
        k::Kernel{F,S}
        x::X
    end
\end{verbatim}
